### 2016-09-29 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Moved Craig's name to acknowledgements

\headerC{
{
\flushright{
Joseph M. Willi \\
Craig G. Weinschenk \\
\vspace*{2\baselineskip}

@@

\headerC{
\flushright{
Joseph M. Willi \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\chapter*{\centering Abstract}
\pagenumbering{gobble}
Nine full-scale fire experiments were conducted in two residential-scale structures to measure the effect of passive and forced ventilation on the fire conditions. The fires were fueled by three propane burners. Five of the experiments were conducted in a single-story structure, and four were conducted in a two-story structure. The structures were instrumented to measure temperature, gas velocity, heat flux, and oxygen, carbon dioxide and carbon monoxide concentrations. Various doors and vents were opened and closed during the experiments to provide passive horizontal and vertical ventilation. A fan was used to provide forced ventilation. This report contains detailed descriptions of the setup and procedure used for each of the nine experiments.

@@

% The ceiling height of each compartment within the structures was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run.

@@

% The exterior doors were made of steel and the stairwell door on the second level of the West Structure was made of lauan plywood.
% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to

@@

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\label{chap:acknowledgments}
The authors would like to thank Daniel Madrzykowski, Roy McLane, Kristopher Overholt, and Keith Stakes for their contributions in preparing and conducting these experiments.

>>>>

\headerC{
{
\flushright{
Joseph M. Willi \\
\vspace*{2\baselineskip}

@@

\headerC{
\flushright{
Joseph M. Willi \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\chapter*{\centering Abstract}
\pagenumbering{gobble}
Nine full-scale fire experiments were conducted in two residential-scale structures to measure the effect of passive and forced ventilation on the fire conditions. The fires were fueled by three propane burners. Five of the experiments were conducted in a single-story structure, and four were conducted in a two-story structure. The structures were instrumented to measure temperature, gas velocity, heat flux, and oxygen, carbon dioxide, and carbon monoxide concentrations. Various doors and vents were opened and closed during the experiments to provide passive horizontal and vertical ventilation. A fan was used to provide forced ventilation. This report contains detailed descriptions of the setup and procedure used for each of the nine experiments.

@@

@@

@@

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\label{chap:acknowledgments}
The author would like to thank Daniel Madrzykowski, Roy McLane, Kristopher Overholt, Keith Stakes, and Craig Weinschenk for their contributions in preparing and conducting these experiments.
